SIPESCA-B: a set of real data time series benchmark for traffic prediction

### 2015-06-14 paper.tex
arreglando el abstract

In the field of traffic management and prediction                     % management? Prediction? Traffic what? Rate? modelling? 
no public real-data benchmarks are available to the research
community                                                              % that we know of, siempre
for testing their information processing methods and compare their
results with those obtained by other researchers.                       % This implies that... or this is bad because... - JJ

In this work the benchmark SIPESCA-B, a set of time series 
obtained monitoring the traffic at several locations in the 
Andalusian road network, is presented. 
Time series are built using real data from the number of vehicles that
have passed through certain locations along several months.             % not _all_ vehicles - JJ
The datasets are provided in simple formats with widespread use and
are left available in a public repository. 
Our aim for this work is to provide public access and details of this benchmark
as well as preliminary results with various prediction methods to the
research community to serve as comparison of future results in the field of
management and traffic prediction.

@@

However, in other areas there is a need for this type of real problems, such as in the area of traffic management.
In this area, due to the type of problems, there is a difficulty in obtaining and using real data.
In some cases due to the lack of data in a suitable format \cite{Flyvbjerg2008}, and in other cases because it is confidential commercial data \cite{Bain2009} obtained, i.e., in highway tolls \cite{Kriger2006}. 
Thus, only certain research works can use that data, which makes impossible to compare results with other researchers.

>>>>

In the field of traffic management and prediction                     % management? Prediction? Traffic what? Rate? modelling? 
no public real-data benchmarks are available to the research
community                                                              % that we know of, siempre
for testing their information processing methods and compare their
results with those obtained by other researchers.                       % This implies that... or this is bad because... - JJ
Sometimes either no data in a suitable format is available or incomplete data makes unable solving the problem at hand. 
In other cases, confidentiality of commercial data reduces the availability of data to a few researchers. 
This limits the access to data and reproducibility of results.
In this work the benchmark SIPESCA-B, a set of time series 
obtained monitoring the traffic at several locations in the 
Andalusian road network, is presented. 
Time series are built using real data from the number of vehicles that
have passed through certain locations along several months.             % not _all_ vehicles - JJ
The datasets are provided in simple formats with widespread use and
are left available in a public repository. 
Our aim for this work is to provide public access and details of this benchmark
as well as preliminary results with various prediction methods to the
research community to serve as comparison of future results in the field of
management and traffic prediction.

@@

However, in other areas there is a need for this type of real problems, such as in the area of traffic management and prediction.
In this area, due to the type of problems, there is a difficulty in obtaining and using real data.
In some cases due to the lack of data in a suitable format \cite{Flyvbjerg2008}, and in other cases because it is confidential commercial data \cite{Bain2009} obtained, i.e., in highway tolls \cite{Kriger2006}. 
Thus, only certain research works can use that data, which makes impossible to compare results with other researchers.
